# 第1章：统计分析与R语言 {#ch1}

本章从统计分析入手，首先介绍了统计分析的四个主要步骤：了解业务问题、数据收集及清洗、数据描述及探索分析，以及模型构建及解读。在统计分析实务中，以上四个步骤必不可少。接下来，在1.2节中介绍了R语言，包括R的下载与安装、如何使用以及如何用好R这一利器。这也是本书接下来各章节中配套使用的编程语言。R语言具备使用广泛、扩展便捷等诸多优势。

<!-- If you need PDF output, uncomment bookdown::pdf_book above in YAML. You will need a LaTeX installation, e.g., https://yihui.name/tinytex/ -->

这里测试`plot`结果：
You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

